\tool

### 2018-02-21 paper/paper.tex

\documentclass[conference]{IEEEtran}
\usepackage{pdftexcmds}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{tool-recommender-bot}
\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}

@@

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interactions}, is the most effective mode of tool discovery\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed \textit{\tool}, a system to automatically recommend development tools. Our system makes recommendations by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their work by automatically running tools and making customized recommendations to developers on GitHub\footnote{https://github.com} projects. This paper seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source static analysis tool for Java code. We examined how often recommendations were made and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

@@

\section{Tool}
Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.s

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase awareness of these tools to improve software quality and developer productivity, ultimately meeting users' and developers' desire for less buggy software.

To target this desire of mistake-free code, our initial implementation of \tool~automatically recommends the tool \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool created by Google to check for errors in Java code based on a suite of bug patterns. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}. \\

@@

To choose a familiar audience, our approach makes recommendations on Github\footnote{https://github.com}, a popular source code management and version control website that hosts millions of projects and serves millions of users. \tool~makes its recommendations on pull requests, or proposed changes to source code submitted by programmers. Developers making these changes should be knowledgeable about the changes they propose as well as the code base to which they are contributing. Our approach suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull requests but still exists elsewhere in the code to capitalize on their familiarity with the modifications and encourage the use of static analysis tools to find more bugs.

@@

\tool~builds on four key concepts to automatically recommend tools to users and improve tool discovery based on our design goals for targeting developer receptivity.

@@

Our system utilizes continuous integration to recommend useful tools before pull request changes are integrated into the main repository, or merged. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes. When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend \textsc{Error Prone}.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject \textsc{Error Prone} as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.

\pseudosubsection{Fix Identification}

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request. \textsc{Error Prone} identifies faults found in the source code, and we developed an algorithm using that information to determine if changes made to the code in the head version fix the identified bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.

@@

\pseudosubsection{Fix Localizaton}

When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by \textsc{Error Prone}. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

Code reviews from co-workers are often standard practice in software development. Pull requests are the primary method of code contributions and code reviews on Github~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request. \tool~automatically runs \textsc{Error Prone} and analyzes the code, providing feedback to developers based on their changes and the output of the tool. Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends \textsc{Error Prone} as a comment at the fix location line from the previous step. Additionally, our system  uses language similar to comments between co-workers in recommendations, such as using ``Good job!'' to compliment developers on their work~\cite{?}.

To further increase adoption and use of static analysis tools, we only make a recommendation if \textsc{Error Prone} reports other instances of the same error in the base version of the code. In the comment, \tool~automatically adds direct links to at most two separate locations where the defect that was fixed still exists in the code. We hope this encourages the developer receiving the recommendation to use \textsc{Error Prone} to fix similar errors and prevent more bugs from being merged into the master code base. Figure 1 presents an example recommendation from our system on a pull request review.
%TODO: Add screenshot

@@

>>>>

\documentclass[conference]{IEEEtran}
\usepackage{pdftexcmds}
\usepackage[pdftex]{graphicx}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{balance}
\usepackage{amssymb, marvosym}
\usepackage{threeparttable}
\usepackage[bookmarks=false]{hyperref}
\usepackage{url}
\PassOptionsToPackage{hyphens}{url}
\hypersetup{colorlinks=true,breaklinks=true}
\usetikzlibrary{patterns,shapes,arrows}
\newcommand\tab[1][.5cm]{\hspace*{#1}}
\hyphenation{op-tical net-works semi-conduc-tor}
\raggedbottom
\newcommand{\tool}{\textsl{tool-recommender-bot}}
\newcommand{\pseudosection}[1]{\vspace{2mm} \noindent {\bf #1}}
\newcommand{\pseudosubsection}[1]{\vspace{2mm} \noindent{\it #1}}

@@

Althouth quality is a primary concern for software engineers and users, developers rarely use tools designed to improve code~\cite{Johnson2013Why}. There are many barriers to tool adoption, and one of the primary reasons useful tools are underused or ignored is the discoverability barrier, or when users are unaware of a tool's existence~\cite{Murphy-HillScreencastingDiscovery}. This lack of awareness for software engineering tools can lead to poor code quality, harmed users, and significant amounts of time and money spent fixing errors. While many automated approaches have been developed to increase knowledge of useful software tools and features, Murphy-Hill and colleagues found that learning about tools from colleagues during normal work activities, or \textit{peer interaction}, is the most effective mode of tool discovery~\cite{MurphyHill2011PeerInteraction}.

To help solve the tool discovery problem among software engineers, we developed \tool. Our system automatically recommends development tools by integrating characteristics of peer interactions and software engineering practices. \tool~is designed for toolsmiths to increase awareness of their products by systematically running their tools and making customized recommendations to developers on GitHub\footnote{https://github.com}, the largest code hosting platform in the world~\cite{GousiosGitHub}. This paper seeks to answer the following research questions (RQs): \\

@@

To answer these questions, we evaluated \tool~by recommending \textsc{Error Prone}\footnote{http://errorprone.info}, an open source Java static analysis tool. We examined how often recommendations were made and how developers reacted to receiving suggestions from our system. This research makes the following contributions:

@@

\section{Tool}
Our approach to improving tool discovery, \tool, aims to increase awareness and use of programming tools among software developers. This section describes the design and implementation of our system.

@@

The primary desire of software users is to have enjoyable and problem-free experiences with software. Developers of these applications also have similar desires, to create high-quality and functioning programs for users. A 2002 study revealed that software engineers demonstrate this desire by spending the majority of the software development process and 70-80\% of their time testing and debugging code~\cite{NIST}. To aid developers in finding, fixing, and preventing various issues in code, many different types of tools have been created to help accomplish these tasks. However, despite the existence of effective tools for detecting errors, the number of bugs in software is increasing~\cite{HaveThingsChanged}. We aim to increase tool discovery by recommending software engineering tools designed to improve software quality. \\

@@

@@

\tool~incorporates key software engineering industry concepts to improve tool discovery among software developers.

@@

Our system utilizes continuous integration to recommend useful tools before pull request changes are integrated into the main repository, or merged. \tool~is implemented as a plugin for Jenkins, ``the leading open source automation server'' for source code deployment and delivery.\footnote{https://jenkins.io/} The system uses Jenkins to clone Github repositories and periodically check for newly-opened pull requests every 15 minutes. When a new pull request is found, our system uses Jenkins to automatically run our approach to recommend useful software engineering tools.

To analyze the source code, we target projects that use the Maven~\footnote{https://maven.apache.org/} build automation and software management tool for Java applications. Our approach uses Maven to automatically handle dependencies and perform the static analysis when the project builds. We inject the desired software engineering tool as a Maven plugin to repository's \textit{pom.xml} project object model file to add it to the build process. \tool~then builds both the original version of the code before the proposed changes were made (base) and the changed version of the repository with the pull request modifications implemented (head) to inspect differences. Using Maven allows \tool~to run on a large number of Java projects that use the popular build tool and also makes our approach extendable to recommend other tools implemented as Maven plugins in future work.

\pseudosubsection{Patch Identification}

After analyzing the base and head versions of the code, our approach parses the build output of each version to determine if any reported errors were fixed in the pull request. The software engineering tool identifies faults in the source code, and we take the tool's output and use it in an algorithm we developed to determine if pull request changes fix a reported bug. Our technique uses the code differencing tool GumTree~\cite{GumTree} to identify actions (addition, delete, insert, move, and update) performed between pull request versions and parse the code to convert the text into abstract syntax trees.

@@

%\pseudosubsection{Fix Localizaton}
%
%When a fix is identified in the pull request, \tool~then aims to find the location of the fix in the head version. To find the modified line that fixed a bug, we use GumTree to parse the Java file and convert it into abstract syntax trees. We look for the action closest to the offset of the error node calculated from the bug line number reported by the software engineering tool, if applicable. If the closest action is not a delete, then our approach take the location takes the location of that action. Otherwise, if the line was removed our algorithm searches for the closest sibling node or if none exists then the location of the parent. Additionally, the line of the fix had to be converted to the equivalent position in the pull request diff file displaying the changes between file versions, or number of lines below the "@@" header\footnote{https://developer.github.com/v3/pulls/comments/\#create-a-comment}, before moving on to the next phase.

@@

Code reviews from co-workers are often standard practice in software development~\cite{CBirdCodeReviewingTrenches}. Pull requests are the primary method of development contributions and code reviews on Github~\cite{PullRequestReview}. Our approach simulates peer reviews by making recommendations for static analysis tools as a comment to the pull request. \tool~automatically runs software engineering tools and analyzes the code changes, providing feedback to developers based on their changes based on the output from the tool. Github provides functionality for making comments at specific lines of code in a pull request, and \tool~recommends the tool as a comment at the fix location line from the previous step. Figure 1 presents an example recommendation from our system on a pull request. %TODO: Add screenshot

To increase the likelihood of tool adoption, our system makes recommendations if the tool reports other instances of the fixed error in the latest version of the code. In the comment, \tool~automatically adds direct links to at most two separate locations of the same defect. Our hope is that this encourages developers to use software engineering toolsin their work to fix the similar errors and prevent additional bugs. Additionally, our system uses language similar to a colleage in recommendations. For instance, \tool~uses ``Good job!'' to compliment developers for fixing an error in their work~\cite{?}.

@@

\subsection{Receptiveness}

Our goal is for \tool~to increase awareness of software engineering tools. For our initial evaluation in this paper, we target software engineers' desire to produce mistake-free code by automatically recommending \textsc{Error Prone}. \textsc{Error Prone} is a static analysis tool that uses a suite of defined bug patterns to detect errors in Java code. Static analysis tools like \textsc{Error Prone} are useful for debugging and preventing errors in source code for applications, however they are often underutilized by software engineers~\cite{Johnson2013Why}.

To choose a familiar audience, our approach makes recommendations on Github pull requests, or proposed code changes submitted by users. Developers should be knowledgeable and familiar with the changes they propose, as well as the code base to which they are contributing. \tool~suggests \textsc{Error Prone} when a reported error is fixed by a developer in a pull request but exists elsewhere in the code.
